\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,                % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font. comment this line out if you want to use the default LaTeX font Computer Modern
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[hidelinks]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\usepackage{mfirstuc}               % enable uppercasing first letter of references
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering

% bibliography
\usepackage[backend=bibtex,style=numeric,sorting=none]{biblatex} % Sorting=none keeps order as cited

\renewbibmacro{in:}{} % Remove "In:" from references

\renewbibmacro*{title}{%
  \ifboolexpr{ test {\iffieldundef{url}} } % Check if URL exists
    {\printfield{title}} % If no URL, just print the title normally
    {\href{\thefield{url}}{\printfield{title}}} % Otherwise, make it a hyperlink
}

\bibliography{bibliography}

\DeclareCiteCommand{\citea}
  {\boolfalse{citetracker}\boolfalse{pagetracker}\usebibmacro{prenote}}
  {\underline{\href{\thefield{url}}{\strfield{subtitle}}}}
  {\multicitedelim}
  {\usebibmacro{postnote}}

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=7pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Brendan Devenney}

\vspace{5pt}

% contact information
\centerline{\href{mailto:hey@devenney.io}{hey@devenney.io} | \href{https://devenney.io}{devenney.io} | \href{https://github.com/devenney}{github.com/devenney}}

\vspace{-10pt}

% experience section
\section*{Experience}

\textbf{Head of Engineering,} \href{https://form3.tech/}{Form3} -- Remote \hfill Nov 2022 -- Present \\
\vspace{-9pt}
\begin{itemize}
  \item Led technical strategy and delivery of SEPA Instant, Credit Transfer, and Direct Debit, via RT1 and STEP2. \\
  \item Processed \citea{klarna} at scale for 150M+ customers across more than 500,000 merchants. \\
  \item Drove the vision and development of \citea{swift}, a novel cloud-native Swift connectivity solution. \\
  \item Spearheaded a new SEPA liqudity model with \citea{barclays}, expanding fintech access to real-time payments. \\
  \item Managed and scaled a 25-engineer team across three squads, serving as a manager-of-managers. \\
  \item Owned end-to-end hiring, mentored via the GROW model, and liaised with customers, vendors, and C-suite. \\
  \item Optimised engineering budgets, reducing costs by 50\% while exceeding customer SLAs. \\
\end{itemize}

\textbf{Lead Software Engineer,} \href{https://form.tech/}{Form3} -- Remote \hfill Jul 2021 -- Nov 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Architected and led development of highly available message brokers for \citea{payport}. \\
  \item Presented Form3's cutting edge solution at \citea{haproxyconf2021}. \\
  \item Collaborated cross-functionally with enterprise customers to seamlessly migrate Faster Payments infrastructure. \\
\end{itemize}

\textbf{Senior Software Engineer,} \href{https://form3.tech/}{Form3} -- Remote \hfill May 2019 -- Jul 2021 \\
\vspace{-9pt}
\begin{itemize}
  \item Contributed to Form3's platform as a backend engineer. \\
\end{itemize}

\textbf{Cloud Improvement Engineer,} \href{https://eviden.com/about-us/legacy-brands/cloudreach/}{Cloudreach} -- Edinburgh, UK \hfill Mar 2018 -- May 2019 \\
\vspace{-9pt}
\begin{itemize}
  \item Consulted for enterprise clients, coaching Agile methodologies while optimising cloud architecture. \\
\end{itemize}

\textbf{Software Engineer,} \href{https://approov.io/}{Approov (\textit{FKA CriticalBlue})} -- Edinburgh, UK \hfill Jul 2013 -- Feb 2018 \\ 
\vspace{-9pt}
\begin{itemize}
  \item Brought a novel Runtime Application Self-Protection (RASP) product to market for \citea{bmw} and \citea{sixt} \\
\end{itemize}

% skills section
\section*{Skills}
\textbf{Leadership:} Technical Strategy, Performance Management, Reliability Engineering, Scaling Teams \\
\textbf{Architecture:} API Design, Distributed Systems, Event-Driven Architectures, High-Throughput Messaging \\  
\textbf{Software Development:} Go, Python, Cloud-Native Development, Defensive Programming, Design Patterns \\
\textbf{Infrastructure:} Kubernetes, Terraform, Observability, CI/CD, High-Availability Systems, Fault Tolerance \\
\textbf{Payments:} FPS, SEPA, Swift, Real-Time Payments, ISO 20022, Scheme Connectivity \\

\vspace{-6.5pt}



% skills section
\section*{Certifications}
\textbf{Professional Scrum Master™ I (PSM I)} \hfill \href{https://www.credly.com/users/devenney}{Scrum.org, 2018} \\
\textbf{TQUK Level 3 Certificate in Understanding Mental Health (RQF)} \hfill West College Scotland, 2022 \\
\textbf{AWS Certified Solutions Architect – Professional} \hfill \href{https://www.credly.com/users/devenney}{AWS Training and Certification, 2018} \\

\vspace{-6.5pt}

% projects section
\section*{Projects}
\begin{itemize}
  \item \underline{\href{https://github.com/oneirism/reverie}{Reverie}:} Tabletop RPG campaign tracker built for game masters, built with Django.
  \item \underline{\href{https://github.com/oneirism/dicebot}{Dicebot}:} Serverless Telegram bot for polyhedral dice rolling, built with Python.
  \item Open source contributor to \underline{\href{https://github.com/hashicorp/packer}{Hashicorp Packer}} and \underline{\href{https://github.com/elastic/beats}{Elastic Beats}}.
\end{itemize}

\vspace{-18.5pt}

% education section
\section*{Volunteering}
\textbf{Stemette Futures} (Education) -- Mentor \hfill Jul 2021 -- Present \\
\textbf{Empty Kitchens, Full Hearts} (Poverty Alleviation) -- Delivery Driver \hfill Apr 2021 -- Present \\

\vspace{-6.5pt}

% education section
\section*{Education}
\textbf{Edinburgh Napier University} -- BEng Software Engineering -- \textit{First Class Honours, Class Medal} \hfill 2016 \\

\end{document}
